Two-Dimensional Vesicle Hydrodynamics from Hydrophobic Attraction Potential

### 2022-02-15 doc/main_jfm.tex
main, refs, Review1,3

The base-case is a single JP vesicle consisting of $N_b = 58$ particles
with $c = 0.5 l_0$ for particle radius, $\rho = 2 l_0$ for decay length,
$\gamma = \text{4.1 pN nm}^{-1}$ for interfacial tension.
The parameter $\mu = \text{1 cP} = \text{1 pN
ns nm}^{-2}$ is viscosity of room-temperature water. 
\ReviewerThree{
  We select \ReviewerOne{$M=4.0$~$\text{pN}$} and $\rho_0 = 0.2l_0$ so that \eqref{eq:REPULforce}
  prevents particle collisions and is comparable to hydrodynamic lubrication.
  \cite{cawthorn_balmforth_2010} provide the asymptotic expression 
  $F_{\text{lubr}} = -\tfrac{3}{2}\pi \mu \dot \epsilon (c/\epsilon)^{3/2}$
  for the lubrication force between two cylinders in the distance of separation $\epsilon \to 0$.
  For our choice of simulation parameters, $F_{\text{lubr}}$ and \eqref{eq:REPULforce} are comparable
  because the particle gaps smaller than the particle radius
  and the relative velocities $\dot \epsilon$ between particles are on
  the order of nm $\text{ns}^{-1}$.
}

>>>>

The base-case is a single JP vesicle consisting of $N_b = 58$ particles
with $c = 0.5 l_0$ for particle radius, $\rho = 2 l_0$ for decay length,
$\gamma = \text{4.1 pN nm}^{-1}$ for interfacial tension.
The parameter $\mu = \text{1 cP} = \text{1 pN
ns nm}^{-2}$ is viscosity of room-temperature water. 
\ReviewerThree{
  We select \ReviewerOne{$M=4.0$~$\text{pN}$} and $\rho_0 = 0.2l_0$ so that \eqref{eq:REPULforce}
  prevents particle collisions and is comparable to hydrodynamic lubrication.
  \cite{cawthorn_balmforth_2010} provide the asymptotic expression 
  $F_{\text{lubr}} = -\tfrac{3}{2}\pi \mu \dot \epsilon (c/\epsilon)^{3/2}$
  for the lubrication force between two cylinders in the distance of separation $\epsilon \to 0$.
  For our choice of simulation parameters, $F_{\text{lubr}}$ and \eqref{eq:REPULforce} are comparable
  because the particle gaps are comparable to the particle radius
  and the relative velocities $\dot \epsilon$ between particles are on
  the order of nm $\text{ns}^{-1}$.
}
